---
title: "Predicting Upcoming Board Games"
author: "Phil Henrickson"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: TRUE #adds a Table of Contents
    number_sections: TRUE #number your headings/sections
    toc_float: TRUE #let your ToC follow you as you scroll
    theme: cerulean #select a different theme from the default
    keep_md: no
    fig.caption: yes
header-includes:
 \usepackage{float}
# knit: (function(input_file, encoding) {
#   out_dir <- 'docs';
#   rmarkdown::render(input_file,
#  encoding=encoding,
#  output_file=file.path(dirname(input_file), out_dir, 'top_upcoming_games.html'))})
# knit: (function(input_file, encoding) {
#         out_dir <- 'docs';
#         rmarkdown::render(
#         input = here::here('production', 'run_predict_bgg_outcomes.Rmd'),
#         encoding = encoding,
#         output_dir = here::here('docs'),
#         output_file = 'top_upcoming_games.html'
#         )})
---

```{r global settings, echo=F, warning=F, message=F, results='hide'}

knitr::opts_chunk$set(echo = F,
                      error=F,
                      dev="png",
                      fig.width = 10,
                      fig.height = 8,
                      fig.pos = 'H')

options(knitr.duplicate.label = "allow")

```


```{r get functions, warning = F, message=F, results = 'hide', include=FALSE}

# get functions
source(here::here("scripts/load_packages.R"))
source(here::here("functions/get_bgg_data_from_github.R"))
source(here::here("functions/get_bgg_data_from_api.R"))
source(here::here("functions/convert_bgg_api_data_to_tables.R"))
source(here::here("functions/predict_bgg_outcomes.R"))
source(here::here("functions/average_col_func.R"))
source(here::here("functions/bayesaverage_col_func.R"))
source(here::here("functions/complexity_col_func.R"))

```

```{r get models, warning = F, message=F, results = 'hide', include=FALSE}

average_workflow = readr::read_rds(here::here("experiments/final_average_xgbTree_fit.Rds"))
complexity_workflow = readr::read_rds(here::here("experiments/final_complexity_xgbTree_fit.Rds"))
usersrated_workflow = readr::read_rds(here::here("experiments/final_usersrated_xgbTree_fit.Rds"))
template_average = readr::read_rds(here::here("experiments/final_template_average.Rds"))
template_usersrated= readr::read_rds(here::here("experiments/final_template_usersrated.Rds"))

```

```{r get games from selected years}

# get games from today
bgg_today = get_bgg_data_from_github(Sys.Date())

set.seed(5)
ids = bgg_today %>%
        filter(game_release_year==2021 | game_release_year == 2022) %>%
        pull(game_id)

```

```{r push ids through api to get game tables for models, results = 'hide', include = F, warning=F, message=F}

# push through api
api_returned = get_bgg_api_data(ids)

# convert to tabular
api_tables = convert_bgg_api_data_to_tables(api_returned)

# convert to format for model
api_games_info = api_tables$games_info %>%
        mutate(numweights = as.character(numweights)) %>% # for some reason numweights is coming through as a character...?
        bind_rows(., template_average[0,]) %>% # bind to our template format
        select(one_of(names(template_average))) # keep only variables in that format
 
# predict with function
out = predict_bgg_outcomes(api_games_info)

# spread out predictions
spread_out = rbindlist(out) %>%
        spread(outcome, .pred) %>%
        mutate(usersrated = round(exp(usersrated),0),
               usersrated_est_complexity = round(exp(usersrated_est_complexity), 0)) %>%
        mutate(bayesaverage = 
                       ((5.5 * 1000) + (average * usersrated))/
                       (1000 + usersrated)) %>%
        mutate(`bayesaverage_est_complexity` = 
                       ((5.5*1000) + (average_est_complexity * usersrated_est_complexity))/
                                (1000+usersrated_est_complexity)) %>%
        mutate_if(is.numeric, round, 2) %>%
        select(.row, game_id, 
               average,
               bayesaverage,
               usersrated,
               complexity,
               average_est_complexity,
               bayesaverage_est_complexity,
               usersrated_est_complexity)

# get all predictions
all_preds = api_games_info %>% 
        select(yearpublished, game_id, name) %>%
        left_join(., spread_out,
                  by = "game_id") %>%
        select(yearpublished, game_id, name, everything()) %>%
        arrange(desc(bayesaverage_est_complexity)) %>%
        mutate(date = Sys.Date()) %>%
        select(date, everything())

# save locally
readr::write_rds(all_preds,
                 file = here::here("predictions", paste("bgg_outcomes_", Sys.Date(), ".Rdata", sep="")))

```

```{r create a function to display table}

# function for geek and average
display_preds_func = function(.preds,
                              est_complexity = T) {
        
        if (est_complexity == T) {
        # display using est complexity
                out = 
                        .preds %>%
                                select(-.row) %>%
                                mutate_at(c("yearpublished", "game_id"),
                                          ~ as.character(.)) %>%
                             #   select(-contains("est_complexity")) %>%
                                mutate(usersrated = plyr::round_any(usersrated, 50),
                                       usersrated_est_complexity = plyr::round_any(usersrated_est_complexity, 50)) %>%
                                rename(Published = yearpublished,
                                       ID = game_id,
                                       Game = name,
                                       Average = average_est_complexity,
                                       GeekRating = bayesaverage_est_complexity,
                                       UserRatings = usersrated_est_complexity,
                                       Complexity = complexity) %>%
                                select(Published, ID, Game, UserRatings, Average, GeekRating, Complexity) %>%
                                mutate(Row = row_number()) %>%
                                select(Row, everything()) %>%
                                flextable() %>%
                                bg(j = "GeekRating",
                                   bg = bayesaverage_col_func) %>%
                                bg(j="Average",
                                  bg = average_col_func) %>%
                                bg(j = "Complexity",
                                   bg = complexity_col_func) %>%       
                                bold(j = c("UserRatings",
                                           "Average",
                                           "GeekRating",
                                           "Complexity"),
                                     part = "header") %>%
                                flextable::align(j = c("UserRatings",
                                                       "Average",
                                                       "GeekRating",
                                                       "Complexity"),
                                                 align = "center",
                                                 part = "all") %>%
                                add_header_row(values = 
                                                       c("",
                                                         "",
                                                         "",
                                                         "",
                                                         "Estimated",
                                                         "Estimated",
                                                         "Estimated",
                                                         "Estimated")) %>%
                                merge_h(part = "header") %>%
                                # hline(j = c("UsersRated",
                                #                          "Average",
                                #                          "GeekRating",
                                #                          "Complexity"), 
                                #       part = "header") %>%
                                autofit()
        
        } else {
                out = 
                        .preds %>%
                                select(-.row) %>%
                                mutate_at(c("yearpublished", "game_id"),
                                          ~ as.character(.)) %>%
                             #   select(-contains("est_complexity")) %>%
                                mutate(usersrated = plyr::round_any(usersrated, 50),
                                       usersrated_est_complexity = plyr::round_any(usersrated_est_complexity, 50)) %>%
                                rename(Published = yearpublished,
                                       ID = game_id,
                                       Game = name,
                                       Average = average,
                                       GeekRating = bayesaverage,
                                       UserRatings = usersrated,
                                       Complexity = complexity) %>%
                                select(Published, ID, Game, UserRatings, Average, GeekRating, Complexity) %>%
                                mutate(Row = row_number()) %>%
                                select(Row, everything()) %>%
                                flextable() %>%
                                bg(j = "GeekRating",
                                   bg = bayesaverage_col_func) %>%
                                bg(j="Average",
                                  bg = average_col_func) %>%
                                bg(j = "Complexity",
                                   bg = complexity_col_func) %>%       
                                bold(j = c("UserRatings",
                                           "Average",
                                           "GeekRating",
                                           "Complexity"),
                                     part = "header") %>%
                                flextable::align(j = c("UserRatings",
                                                       "Average",
                                                       "GeekRating",
                                                       "Complexity"),
                                                 align = "center",
                                                 part = "all") %>%
                                add_header_row(values = 
                                                       c("",
                                                         "",
                                                         "",
                                                         "",
                                                         "Estimated",
                                                         "Estimated",
                                                         "Estimated",
                                                         "Estimated")) %>%
                                merge_h(part = "header") %>%
                                # hline(j = c("UsersRated",
                                #                          "Average",
                                #                          "GeekRating",
                                #                          "Complexity"), 
                                #       part = "header") %>%
                                autofit()
                
        }
        
        return(out)
        
}


# function for table with type
display_preds_func2 = function(.preds,
                               .type,
                              est_complexity = T) {
        
        
        if (est_complexity == T) {
        # display using est complexity
                out = 
                        .preds %>%
                                select(-.row) %>%
                                mutate_at(c("yearpublished", "game_id"),
                                          ~ as.character(.)) %>%
                             #   select(-contains("est_complexity")) %>%
                                mutate(usersrated = plyr::round_any(usersrated, 50),
                                       usersrated_est_complexity = plyr::round_any(usersrated_est_complexity, 50)) %>%
                                rename(Published = yearpublished,
                                       ID = game_id,
                                       Game = name,
                                       Average = average_est_complexity,
                                       GeekRating = bayesaverage_est_complexity,
                                       UserRatings = usersrated_est_complexity,
                                       Complexity = complexity) %>%
                                select(Published, ID, Game, UserRatings, Average, GeekRating, Complexity) %>%
                                mutate(Row = row_number()) %>%
                        mutate(Type = paste(.type)) %>%
                                select(Row, Type, everything()) %>%
                                flextable() %>%
                                bg(j = "GeekRating",
                                   bg = bayesaverage_col_func) %>%
                                bg(j="Average",
                                  bg = average_col_func) %>%
                                bg(j = "Complexity",
                                   bg = complexity_col_func) %>%       
                                bold(j = c("UserRatings",
                                           "Average",
                                           "GeekRating",
                                           "Complexity"),
                                     part = "header") %>%
                                flextable::align(j = c("UserRatings",
                                                       "Average",
                                                       "GeekRating",
                                                       "Complexity"),
                                                 align = "center",
                                                 part = "all") %>%
                                add_header_row(values = 
                                                       c("",
                                                         "",
                                                         "",
                                                         "",
                                                         "",
                                                         "Estimated",
                                                         "Estimated",
                                                         "Estimated",
                                                         "Estimated")) %>%
                                merge_h(part = "header") %>%
                                # hline(j = c("UsersRated",
                                #                          "Average",
                                #                          "GeekRating",
                                #                          "Complexity"), 
                                #       part = "header") %>%
                                autofit()
        
        } else {
                out = 
                        .preds %>%
                                select(-.row) %>%
                                mutate_at(c("yearpublished", "game_id"),
                                          ~ as.character(.)) %>%
                             #   select(-contains("est_complexity")) %>%
                                mutate(usersrated = plyr::round_any(usersrated, 50),
                                       usersrated_est_complexity = plyr::round_any(usersrated_est_complexity, 50)) %>%
                                rename(Published = yearpublished,
                                       ID = game_id,
                                       Game = name,
                                       Average = average,
                                       GeekRating = bayesaverage,
                                       UserRatings = usersrated,
                                       Complexity = complexity) %>%
                                select(Published, ID, Game, UserRatings, Average, GeekRating, Complexity) %>%
                                mutate(Row = row_number()) %>%
                        mutate(Type = paste(.type)) %>%
                                select(Row, Type, everything()) %>%
                                flextable() %>%
                                bg(j = "GeekRating",
                                   bg = bayesaverage_col_func) %>%
                                bg(j="Average",
                                  bg = average_col_func) %>%
                                bg(j = "Complexity",
                                   bg = complexity_col_func) %>%       
                                bold(j = c("UserRatings",
                                           "Average",
                                           "GeekRating",
                                           "Complexity"),
                                     part = "header") %>%
                                flextable::align(j = c("UserRatings",
                                                       "Average",
                                                       "GeekRating",
                                                       "Complexity"),
                                                 align = "center",
                                                 part = "all") %>%
                                add_header_row(values = 
                                                       c("",
                                                         "",
                                                         "",
                                                         "",
                                                         "",
                                                         "Estimated",
                                                         "Estimated",
                                                         "Estimated",
                                                         "Estimated")) %>%
                                merge_h(part = "header") %>%
                                # hline(j = c("UsersRated",
                                #                          "Average",
                                #                          "GeekRating",
                                #                          "Complexity"), 
                                #       part = "header") %>%
                                autofit()
                
        }
        
        return(out)
        
}
```

# What is this analysis? {-}

Which upcoming board games are likely to be highly rated on boardgamegeek.com?

To answer this question, I trained predictive models on historical data from BGG. These models look at information known about a game at the time of its release in order to estimate its eventual average rating, geek rating, complexity, and number of user ratings. For each of these outcomes, I trained models (using gradient boosted trees) on board games published through 2020. I then use the models to estimate BGG outcomes for all upcoming games.

# Top 100 Upcoming Games

What games published in 2021 and 2022 are expected to be the highest rated?

## Geek Rating

What are the top games according to the estimated **geek** rating? The geek rating uses a combination of the average rating and the number of user ratings, so games estimated to be high on the geek rating are expected to be both well rated and popular.

```{r display top 100 for geekrating}

# join back up and take a look
preds = api_games_info %>% 
        select(yearpublished, game_id, name) %>%
        left_join(., spread_out,
                  by = "game_id") %>%
        select(yearpublished, game_id, name, everything()) %>%
        arrange(desc(bayesaverage_est_complexity)) %>%
        head(100)

# make table
display_preds_func(.preds = preds,
                   est_complexity=T)

```

## Average Rating

What are the top games according to the estimated **average** rating? This rating is simply the average of all ratings assigned to a game by BGG users. The top games by this metric are games that are expected to be very well rated, even if by only a small set of users. 

```{r display top 100 for average} 

# join back up and take a look
preds = api_games_info %>% 
        select(yearpublished, game_id, name) %>%
        left_join(., spread_out,
                  by = "game_id") %>%
        select(yearpublished, game_id, name, everything()) %>%
        arrange(desc(average_est_complexity)) %>%
        head(100)

# make table
display_preds_func(.preds = preds,
                   est_complexity=T)

```

# Top Upcoming Games by Category

We can examine this further by looking at the top games within particular categories using the estimated average rating. 

## Fantasy

```{r top 50 for fantasy}

# join back up and take a look
preds = api_games_info %>% 
        filter(category_fantasy == 1) %>%
        select(yearpublished, game_id, name) %>%
        left_join(., spread_out,
                  by = "game_id") %>%
        select(yearpublished, game_id, name, everything()) %>%
        arrange(desc(average_est_complexity)) %>%
        head(50)

# make table
display_preds_func2(.preds = preds,
                   .type = 'Fantasy',
                   est_complexity=T)

```


## Economic

```{r top 50 for economic}

# join back up and take a look
preds = api_games_info %>% 
        filter(category_economic == 1) %>%
        select(yearpublished, game_id, name) %>%
        left_join(., spread_out,
                  by = "game_id") %>%
        select(yearpublished, game_id, name, everything()) %>%
        arrange(desc(average_est_complexity)) %>%
        head(50)

# make table
display_preds_func2(.preds = preds,
                   .type = 'Economic',
                   est_complexity=T)

```

## Wargames

```{r top 50 for wargame}

# join back up and take a look
preds = api_games_info %>% 
        filter(category_wargame == 1) %>%
        select(yearpublished, game_id, name) %>%
        left_join(., spread_out,
                  by = "game_id") %>%
        select(yearpublished, game_id, name, everything()) %>%
        arrange(desc(average_est_complexity)) %>%
        head(50)

# make table
display_preds_func2(.preds = preds,
                   .type = 'Wargame',
                   est_complexity=T)

```

## Party

```{r top 50 for party games}

# join back up and take a look
preds = api_games_info %>% 
        filter(category_party_game == 1) %>%
        select(yearpublished, game_id, name) %>%
        left_join(., spread_out,
                  by = "game_id") %>%
        select(yearpublished, game_id, name, everything()) %>%
        arrange(desc(average_est_complexity)) %>%
        head(50)

# make table
display_preds_func2(.preds = preds,
                   .type = 'Party',
                   est_complexity=T)

```

## Cardgames

```{r top 50 for card games}

# join back up and take a look
preds = api_games_info %>% 
        filter(category_card_game == 1) %>%
        select(yearpublished, game_id, name) %>%
        left_join(., spread_out,
                  by = "game_id") %>%
        select(yearpublished, game_id, name, everything()) %>%
        arrange(desc(average_est_complexity)) %>%
        head(50)

# make table
display_preds_func2(.preds = preds,
                   .type = 'Cardgame',
                   est_complexity=T)

```

# All Upcoming Games

The tables above showed only a portion of all games that the model looked at. The table below is interactive and allows users to search for specific games and sort by the outcome they are most interested in.

```{r interactive table for all upcoming}

# All Upcoming Games

# All Upcoming Ga
DT::datatable(all_preds %>%
                      select(-date) %>%
                      select(-.row) %>%
                      mutate_at(c("usersrated", "usersrated_est_complexity"),
                                ~ plyr::round_any(., 50, ceiling)) %>%
                      mutate_at(c("yearpublished", "game_id"),
                                          ~ as.character(.)) %>%
                      rename(Published = yearpublished,
                             ID = game_id,
                             Name = name,
                             Average = average_est_complexity,
                                    GeekRating = bayesaverage_est_complexity,
                                    UserRatings = usersrated_est_complexity,
                                    Complexity = complexity) %>%
                      select(Published, 
                             ID,
                             Name,
                             UserRatings,
                             Average,
                             GeekRating,
                             Complexity))
```


```


