---
title: "Examining BGG Rating Models"
author: Phil Henrickson
date: "`r Sys.Date()`"
output: 
  html_document:
        toc: true
        toc_depth: 2
        number_sections: true
---

```{r global settings, echo=F, warning=F, message=F}

knitr::opts_chunk$set(echo = F,
                      error=F,
                      dev="png",
                      fig.width = 10,
                      fig.height = 6)

options(knitr.duplicate.label = "allow")
options(scipen=999)

source(here::here("scripts/load_packages.R"))
source(here::here("functions/theme_phil.R"))

```

```{r flextable settings, echo=F, warning=F, message=F}

library(flextable)
set_flextable_defaults(theme_fun = theme_alafoli,
                       font.color = "grey10",
  padding.bottom = 6, 
  padding.top = 6,
  padding.left = 6,
  padding.right = 6,
  background.color = "white")

```

```{r get function, echo=F, warning=F, message=F}

# function for loading game by id
source(here::here("functions/get_game_record.R"))

# function for reading in current bgg data
source(here::here("functions/get_bgg_data_from_github.R"))

# function for predicting with trained model
source(here::here("functions/bake_and_predict_ratings.R"))

# function for predicting with stan
source(here::here("functions/bake_and_predict_posterior.R"))

# function for plotting posterior
source(here::here("functions/plot_posterior.R"))

# function for predicting complexity then ratings
source(here::here("functions/bake_and_predict_avgweight_and_ratings.R"))

# function for renaming and tidying output
source(here::here("functions/rename_func.R"))
source(here::here("functions/baverage_func.R"))
source(here::here("functions/average_func.R"))
source(here::here("functions/avgweight_func.R"))

```

```{r get todays bgg data then filter to year, echo=F, warning=F, message=F}

# get todays data from bgg
bgg_today<-get_bgg_data_from_github(Sys.Date()) %>%
        group_by(game_id) %>%
        filter(users_rated == max(users_rated)) %>% # make sure we're taking the max entry for each game, as there are some dupes
        ungroup()

```

```{r function for converting to table}

display_preds = function(input_preds,
                         bgg_today) {
        
        # get estimates
        estimated = input_preds$estimate %>%
                mutate(type = 'est') %>%
                select(yearpublished, game_id, name, type, outcome, pred) %>%
                rename(value = pred) %>%
                as_tibble()

        # get current
        current = bgg_today %>%
                filter(game_release_year %in% unique(input_preds$estimate$yearpublished)) %>%
                select(game_id, game_name, game_release_year, bgg_average, bayes_average, users_rated) %>%
                rename(name = game_name,
                       average = bgg_average,
                       baverage = bayes_average,
                       yearpublished = game_release_year,
                       usersrated = users_rated) %>%
                melt(., id.vars = c("game_id", "name", "yearpublished")) %>%
                rename(outcome = variable) %>%
                mutate(type = "actual") %>%
                select(yearpublished, game_id, name, type, outcome, value) %>%
                as_tibble() 
        
        # bind with current
        combined = bind_rows(estimated, current)
        
        # convert for table
        table = combined %>%
                pivot_wider(names_from = c("type", "outcome"),
                            values_from = c("value")) %>%
               #             values_fn = length) %>%
                rename(usersrated = actual_usersrated,
                       average = actual_average,
                       baverage = actual_baverage) %>%
                select(yearpublished,
                       game_id, name, 
                       usersrated, 
                       est_average,
                       average, 
                       est_baverage,
                       baverage) %>%
                mutate(yearpublished = as.character(yearpublished),
                       game_id = as.character(game_id)) %>%
                mutate_if(is.numeric, round, 2)
        
        # flextable
        ft_table = table %>%
             #   select(-usersrated) %>%
                rename(Published = yearpublished,
                       ID = game_id,
                       Ratings = usersrated,
                       Name = name) %>%
                arrange(desc(est_baverage)) %>%
                rename(Predicted = est_average,
                       Actual = average,
                       `Predicted `= est_baverage,
                       `Actual ` = baverage) %>%
                mutate(Row = row_number()) %>%
                select(Row, everything()) %>%
                flextable() %>%
                flextable::autofit() %>%
                add_footer(top = T, values = paste("Predictions as of ", Sys.Date())) %>%
                bold(part = "header") %>%
                border_remove() %>%
                bg(., j = c("Predicted ", "Actual "),
                   bg = baverage_func) %>%
                bg(., j = c("Predicted", "Actual"),
                   bg = average_func) %>%
                flextable::align(j = c("Predicted", "Predicted ",
                                       "Actual", "Actual "),
                         align = "center",
                         part = "all") %>%
                add_header_row(values = 
                                       c("",
                                         "",
                                         "",
                                         "",
                                         "",
                                         "Average",
                                         "Average",
                                         "Geek",
                                         "Geek")) %>%
                merge_h(part = "header")

        # add_header(average = "Estimated",
        #            baverage = "Estimated", 
        #            top = TRUE) %>%
        # merge_h(part = "header") %>%
        
        return(ft_table)
        
}

```

# What is this Analyis? {-}

This notebook displays the estimated average, geek rating, and complexity for upcoming games. The model was trained on board games published through 2019, so I display the model's estimates for games published from 2020 and onwards. 

This analysis was run on **`r Sys.Date()`**.

# Estimating Ratings

We can first estimate the average rating and geek rating for all games given the data that is currently available on BGG. That means these sets of estimates make use of the current average weight for the game. This means the models are predicting BGG's rating for a game *given information we already from the community about the game*. For games with relatively few votes, the estimate of a game's average weight may be unreliable.

Additionally, we lose some of our ability to call our work predictive, in that the community's estimate of the weight of a game is an extremely important indicator of how the community rates the game. To address these concerns, in the next section I first estimate the avgweight and then use the estimated value in the model.

## Estimated Ratings for 2020

```{r predict ratings for 2020, echo=F, warning=F, message=F}

# Predict BGG ratings and complexity with previously trained models.

# pull ids
ids = bgg_today %>%
  filter(game_release_year == 2020) %>%
  pull(game_id)

# feed through predictive models to get predictions
preds = bake_and_predict_ratings(ids,
                                         "xgbTree_fit")

```

Plot of predicted vs current

```{r plot 2021, warning=F, message=F, fig.width=10, fig.height=10}

# get estimates
estimated = preds$estimate %>%
        mutate(type = 'est') %>%
        select(yearpublished, game_id, name, type, outcome, pred) %>%
        rename(value = pred) %>%
        as_tibble()

# get current
current = bgg_today %>%
        filter(game_release_year %in% unique(preds$estimate$yearpublished)) %>%
        select(game_id, game_name, game_release_year, bgg_average, bayes_average, users_rated) %>%
        rename(name = game_name,
               average = bgg_average,
               baverage = bayes_average,
               yearpublished = game_release_year,
               usersrated = users_rated) %>%
        melt(., id.vars = c("game_id", "name", "yearpublished")) %>%
        rename(outcome = variable) %>%
        mutate(type = "actual") %>%
        select(yearpublished, game_id, name, type, outcome, value) %>%
        as_tibble() 
        
# bind with current
bind_rows(estimated, current) %>%
               pivot_wider(names_from = c("type"),
                    values_from = c("value")) %>%
        filter(outcome == 'baverage' | 
                       outcome =='average') %>%
        ggplot(., aes(x=est,
                      label = name,
                      y=actual))+
        geom_point(alpha = 0.25)+
        facet_wrap(yearpublished~outcome,
                   ncol = 1,
                   scales = "free")+
        theme_bw(16)+
        geom_abline(slope = 1,
                    intercept = 0)+
        geom_text(check_overlap=T,
                  size = 2,
                  vjust = -1
                  )+
        xlab("Estimated")+
        ylab("Current")
```


```{r use function for table for 2020, warning=F, message=F}

display_preds(preds,
              bgg_today)
 
```

## Estimated Ratings for 2021

```{r predict ratings for 2021, echo=F, warning=F, message=F}

# Predict BGG ratings and complexity with previously trained models.

# pull ids
ids = bgg_today %>%
  filter(game_release_year == 2021) %>%
  pull(game_id)

# feed through predictive models to get predictions
preds = bake_and_predict_ratings(ids,
                                         "xgbTree_fit")

```

Plot of predicted vs current.

```{r plot 2021, warning=F, message=F, eval=F, fig.width=10, eval=F, fig.height=10}

# get estimates
estimated = preds$estimate %>%
        mutate(type = 'est') %>%
        select(yearpublished, game_id, name, type, outcome, pred) %>%
        rename(value = pred) %>%
        as_tibble()

# get current
current = bgg_today %>%
        filter(game_release_year %in% unique(preds$estimate$yearpublished)) %>%
        select(game_id, game_name, game_release_year, bgg_average, bayes_average, users_rated) %>%
        rename(name = game_name,
               average = bgg_average,
               baverage = bayes_average,
               yearpublished = game_release_year,
               usersrated = users_rated) %>%
        melt(., id.vars = c("game_id", "name", "yearpublished")) %>%
        rename(outcome = variable) %>%
        mutate(type = "actual") %>%
        select(yearpublished, game_id, name, type, outcome, value) %>%
        as_tibble() 
        
# bind with current
bind_rows(estimated, current) %>%
               pivot_wider(names_from = c("type"),
                    values_from = c("value")) %>%
        filter(outcome == 'baverage' | 
                       outcome =='average') %>%
        ggplot(., aes(x=est,
                      label = name,
                      y=actual))+
        geom_point(alpha = 0.25)+
        facet_wrap(yearpublished~outcome,
                   ncol = 1,
                   scales = "free")+
        theme_bw(16)+
        geom_abline(slope = 1,
                    intercept = 0)+
        geom_text(check_overlap=T,
                  size = 2,
                  vjust = -1
                  )+
        xlab("Estimated")+
        ylab("Current")
```

In table form.

```{r use function for table for 2021, warning=F, message=F}

display_preds(preds,
              bgg_today)
 
```

## Estimated Ratings for 2022

```{r predict ratings for 2022, echo=F, warning=F, message=F}


# Predict BGG ratings and complexity with previously trained models.

# pull ids
ids = bgg_today %>%
  filter(game_release_year == 2022) %>%
  pull(game_id)

# feed through predictive models to get predictions
preds = bake_and_predict_ratings(ids,
                                         "xgbTree_fit")

```


```{r plot 2021, warning=F, message=F, fig.width=10, fig.height=10}

# get estimates
estimated = preds$estimate %>%
        mutate(type = 'est') %>%
        select(yearpublished, game_id, name, type, outcome, pred) %>%
        rename(value = pred) %>%
        as_tibble()

# get current
current = bgg_today %>%
        filter(game_release_year %in% unique(preds$estimate$yearpublished)) %>%
        select(game_id, game_name, game_release_year, bgg_average, bayes_average, users_rated) %>%
        rename(name = game_name,
               average = bgg_average,
               baverage = bayes_average,
               yearpublished = game_release_year,
               usersrated = users_rated) %>%
        melt(., id.vars = c("game_id", "name", "yearpublished")) %>%
        rename(outcome = variable) %>%
        mutate(type = "actual") %>%
        select(yearpublished, game_id, name, type, outcome, value) %>%
        as_tibble() 
        
# bind with current
bind_rows(estimated, current) %>%
               pivot_wider(names_from = c("type"),
                    values_from = c("value")) %>%
        filter(outcome == 'baverage' | 
                       outcome =='average') %>%
        ggplot(., aes(x=est,
                      label = name,
                      y=actual))+
        geom_point(alpha = 0.25)+
        facet_wrap(yearpublished~outcome,
                   ncol = 1,
                   scales = "free")+
        theme_bw(16)+
        geom_abline(slope = 1,
                    intercept = 0)+
        geom_text(check_overlap=T,
                  size = 2,
                  vjust = -1
                  )+
        xlab("Estimated")+
        ylab("Current")

rm(current, estimated, combined)
```


Table of predictions

```{r use function for table for 2022, warning=F, message=F}

display_preds(preds,
              bgg_today)
 
```

# Estimating Weight and Ratings

These sets of estimates *first* estimate the complexity of a game, and then plug the estimated complexity into the model for predicting the ratings. This means these estimates will be relatively unchanging over time, with the only time varying factor being the year of publication.

```{r function for displaying predictd weight in additiona}

display_preds_with_weights = function(input_preds) {
        
        # get estimates
        estimated = bind_rows(
                        input_preds$estimated_weight %>%
                        mutate(type = 'est') %>%
                        select(yearpublished, game_id, name, type, outcome, pred) %>%
                        rename(value = pred) %>%
                        as_tibble(),
                        input_preds$estimated_rating %>%
                                mutate(type = 'est') %>%
                                select(yearpublished, game_id, name, type, outcome, pred) %>%
                                rename(value = pred) %>%
                                as_tibble())

        # get current
        current = input_preds$actual_weight_and_rating %>%
                select(game_id, name, yearpublished, usersrated, average, baverage, avgweight) %>%
                melt(., id.vars = c("game_id", "name", "yearpublished")) %>%
                rename(outcome = variable) %>%
                mutate(type = "actual") %>%
                select(yearpublished, game_id, name, type, outcome, value) %>%
                as_tibble()

        # bind with current
        combined = bind_rows(estimated, current)
        
        # convert for table
        table = combined %>%
                pivot_wider(names_from = c("type", "outcome"),
                            values_from = c("value")) %>%
                rename(usersrated = actual_usersrated,
                       avgweight = actual_avgweight,
                       average = actual_average,
                       baverage = actual_baverage) %>%
                select(yearpublished,
                       game_id, name, 
                       usersrated,
                       est_average,
                       average, 
                       est_baverage,
                       baverage,
                       est_avgweight,
                       avgweight) %>%
                mutate(yearpublished = as.character(yearpublished),
                       game_id = as.character(game_id)) %>%
                mutate_if(is.numeric, round, 2) 
        
        # flextable
        ft_table = table %>%
                rename(Ratings = usersrated,
                       Published = yearpublished,
                       ID = game_id,
                       Name = name) %>%
                arrange(desc(est_baverage)) %>%
                rename(Predicted = est_average,
                       Actual = average,
                       `Predicted `= est_baverage,
                       `Actual ` = baverage,
                       `Predicted  ` = est_avgweight,
                       `Actual  ` = avgweight) %>%
                mutate(Row = row_number()) %>%
                select(Row, everything()) %>%
                flextable() %>%
                flextable::autofit() %>%
                add_footer(top = T, values = paste("Predictions as of ", Sys.Date())) %>%
                bold(part = "header") %>%
                border_remove() %>%
                bg(., j = c("Predicted ", "Actual "),
                   bg = baverage_func) %>%
                bg(., j = c("Predicted", "Actual"),
                   bg = average_func) %>%
                bg(., j = c("Predicted  ", "Actual  "),
                   bg = avgweight_func) %>%
                flextable::align(j = c("Predicted", "Predicted ", "Predicted  ",
                                       "Actual", "Actual ", "Actual  "),
                         align = "center",
                         part = "all") %>%
                add_header_row(values = 
                                       c("",
                                         "",
                                         "",
                                         "",
                                         "",
                                         "Average",
                                         "Average",
                                         "Geek",
                                         "Geek",
                                         "Complexity",
                                         "Complexity")) %>%
                merge_h(part = "header")
        
        # add_header(average = "Estimated",
        #            baverage = "Estimated", 
        #            top = TRUE) %>%
        # merge_h(part = "header") %>%
        
        return(ft_table)
        
}

```

## Estimated Ratngs and Complexity for 2020

```{r get games and predict both outcomes 2020, echo=F, warning=F, message=F}

# Predict BGG ratings and complexity with previously trained models.
# pull ids
ids = bgg_today %>%
  filter(game_release_year == 2020) %>%
  pull(game_id)

# feed through predictive models to get predictions
preds = bake_and_predict_avgweight_and_ratings(ids,
                                         "xgbTree_fit")

```

```{r display estimates for ratings and weight for 2020}

display_preds_with_weights(preds)

```

## Estimated Ratings and Complexity for 2021

```{r get games and predict both outcomes 2021, echo=F, warning=F, message=F}

# Predict BGG ratings and complexity with previously trained models.
# pull ids
ids = bgg_today %>%
  filter(game_release_year == 2021) %>%
  pull(game_id)

# feed through predictive models to get predictions
preds = bake_and_predict_avgweight_and_ratings(ids,
                                         "xgbTree_fit")

```

```{r display estimates for ratings and weight for 2021}

display_preds_with_weights(preds)

```

## Estimated Ratings and Complexity for 2022

```{r get games and predict both outcomes 2022, echo=F, warning=F, message=F}

# Predict BGG ratings and complexity with previously trained models.
# pull ids
ids = bgg_today %>%
  filter(game_release_year == 2022) %>%
  pull(game_id)

# feed through predictive models to get predictions
preds = bake_and_predict_avgweight_and_ratings(ids,
                                         "xgbTree_fit")

```

```{r display estimates for ratings and weight for 2022}

display_preds_with_weights(preds)

```

Get predictions for all.

```{r get preds for all}

# pull ids
ids = bgg_today %>%
        filter(game_release_year >= 2020 & game_release_year <= 2023) %>%
        pull(game_id)

# xgbTree
# get predictions for all
preds_all_xgbTree = bake_and_predict_ratings(ids,
                                         "xgbTree_fit")

# get predictions for all with weights
preds_weights_all_xgbTree = bake_and_predict_avgweight_and_ratings(ids,
                                         "xgbTree_fit")

# glmnet
# get predictions for all
preds_all_glmnet = bake_and_predict_ratings(ids,
                                         "glmnet_fit")

# get predictions for all with weights
preds_weights_all_glmnet = bake_and_predict_avgweight_and_ratings(ids,
                                         "glmnet_fit")

```

Combine and save output.

```{r combine and save}

preds_out = bind_rows(preds_all_xgbTree$estimate %>%
                              mutate(type = "bgg"),
                      preds_all_glmnet$estimate %>%
                              mutate(type = "bgg"),
                      preds_weights_all_glmnet$estimated_rating %>%
                              mutate(type = "est_avgweight"),
                      preds_weights_all_xgbTree$estimated_rating %>%
                              mutate(type = "est_avgweight"),
                      preds_weights_all_xgbTree$estimated_weight %>%
                              mutate(type = "bgg")) %>%
        as_tibble() %>%
        mutate(method = gsub("_fit", "", method)) %>%
        mutate(date = Sys.Date()) %>%
        select(date, yearpublished, game_id, name, method, type, outcome, pred) %>%
        arrange(game_id, method, outcome)

# write
readr::write_rds(preds_out, file = paste(here::here("predict_ratings/predictions/", paste("preds_", Sys.Date(), ".Rdata", sep=""))))

```

