---
title: "Predicting Upcoming Board Games"
author: "github.com/phenrickson/bgg"
date: "`r Sys.Date()`"
output: 
  html_document
params:
  url: "https://www.reddit.com/r/boardgames/comments/qyu3bq/kickstarter_roundup_nov_21_2021_20_ending_soon/"
---

```{r load and set packages, echo=F, warning=F, message=F,  results = 'hide'}

suppressMessages( {
        
knitr::opts_chunk$set(echo = F,
                      error=F,
                      dev="png",
                      fig.width = 9,
                      fig.height = 6)

options(knitr.duplicate.label = "allow")

options(scipen=999)

source(here::here("scripts/load_packages.R"))
source(here::here("functions/theme_phil.R"))
library(plumber)
library(rvest)
library(htmltab)
library(RCurl)
library(RTidyHTML)
library(XML)
library(htm2txt)

library(webshot2)
library(flextable)
set_flextable_defaults(theme_fun = theme_alafoli,
                       font.color = "grey10",
  padding.bottom = 6, 
  padding.top = 6,
  padding.left = 6,
  padding.right = 6,
  background.color = "white")

# other packages?


})

```


```{r load packages and scrape, warning=F, message=F}

# Input URL and grab games with BGG IDs.

# feed in URL
u = params$url
# get html
doc = read_html(u)
# tree parse
html <- htmlTreeParse(doc, useInternal = TRUE)
# extract links
links <- xpathSApply(html, "//a/@href")
# filter to bgg links
bgg_links = as_tibble(links[grepl("boardgamegeek.com", links)])

# separate and get ids
tidy_bgg_links = bgg_links %>%
        rename(link = value) %>%
        mutate(game = gsub("https://boardgamegeek.com/", "", link)) %>%
        separate(game, c("type", "id", "name"), sep="\\/")

# get post details
tidy_reddit_links = as_tibble(u) %>%
        rename(link = value) %>%
        mutate(post = gsub("https://www.reddit.com/r/boardgames/comments/",
                           "", link)) %>%
        select(post, link) %>%
        separate(post, c("post_id", "post_title"), sep = "\\/") %>%
        mutate(post_date = gsub("crowdfunding_roundup_", "", gsub("_ending_soon", "", gsub("kickstarter_roundup_", "", post_title)))) %>%
        select(starts_with("post_"), everything()) %>%
        mutate(date_char = str_to_title(gsub("_", " ", substr(post_date, 1, 11))))
        
# games
games = tidy_bgg_links %>%
        filter(type == 'boardgame') %>%
        select(type, id, name)

# function for loading game by id
source(here::here("functions/get_game_record.R"))
# function for reading in current bgg data
source(here::here("functions/get_bgg_data_from_github.R"))
# function for predicting with trained model
source(here::here("functions/bake_and_predict_avgweight_and_ratings.R"))
# # function for plotting posterior
# source("functions/plot_posterior.R")

conflict_prefer("set_names", "magrittr")

```


```{r predict, warning=F, message=F, results= 'hide'}

# Predict BGG ratings and complexity with previously trained models.

# pull ids
ids = games %>%
        pull(id)

# feed through predictive models to get predictions
preds_xgbTree = bake_and_predict_avgweight_and_ratings(ids,
                                         "xgbTree_fit")

# estimated weight
complexity = preds_xgbTree$estimated_weight
ratings = preds_xgbTree$estimated_rating

# combine
table = ratings %>%
        spread(outcome, pred) %>%
        select(-method) %>%
        left_join(., 
                  complexity %>%
                          spread(outcome, pred) %>%
                          select(game_id, avgweight),
                  by = "game_id") %>%
        arrange(desc(baverage))

```

### Table of Estimates for Games from `r tidy_reddit_links$date_char`

The table below displays estimated ratings for the boardgamegeek community rating, geek rating, and complexity games from the reddit weekly Kickstarter roundup. These estimates come from models previously trained on historical boardgamegeek data. For more details, see github.com/phenrickson/bgg for more.

Link to Reddit post:`r params$url`

```{r create flextable, warning=F, message=F}

# add color to tables
source(here::here("functions/baverage_func.R"))
source(here::here("functions/average_func.R"))
source(here::here("functions/avgweight_func.R"))

# edit
tidy_table = table %>%
        arrange(desc(average)) %>%
        mutate(Row = row_number()) %>%
        mutate(yearpublished = as.character(yearpublished),
               game_id = as.character(game_id)) %>%
        rename(Published = yearpublished,
               BGG_ID = game_id,
               Game = name) %>%
        mutate(Post_Date = tidy_reddit_links$date_char) %>%
        select(Row, Post_Date,  BGG_ID, Published, Game, average, baverage, avgweight)

# get to ft
ft_table = tidy_table %>%
        flextable() %>%
        flextable::autofit() %>%
        flextable::align(j = c("average", "baverage", "avgweight"),
                         align = "center",
                         part = "all") %>%
        add_header(average = "Estimated",
                   baverage = "Estimated", 
                   avgweight = "Estimated",
                   top = TRUE) %>%
        merge_h(part = "header") %>%
        add_footer(top = F, values = paste("Predictions as of ", Sys.Date())) %>%
        bold(part = "header") %>%
        border_remove() %>%
        bg(., j = c("baverage"),
           bg = baverage_func) %>%
        bg(., j = c("average"),
                   bg = average_func) %>%
       bg(., j = c("avgweight"),
           bg = avgweight_func) %>%
  set_caption("Estimates of BGG Ratings for Kickstarter Games")

# display
ft_table

```


```{r save file}


#readr::write_rds(ft_table, file = paste("kickstarter_roundup_tables/", tidy_reddit_links$post_date, ".Rds", sep=""))
#fwrite(tidy_table, file = paste("kickstarter_roundup_tables/", tidy_reddit_links$post_date, ".csv", sep=""))

```

